--- 
title: "Introduction to Bioinformatics"
author: "Diego Diez"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Material covered in the *Introduction to Bioinformatics* intensive course held in Nagoya University, Dec 13-14, 2017."
---

# About {-}

This manual includes some of the topics covered during the intensive course *Introduction to Bioinformatics* held in at Nagoya University in Dec 13-14, 2017. It does not try to be particularly comprehensive but serve as a small guide for the students.

# Prerequisites {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

